---
title: "Assignment"
subtitle: "Course Name"
author: "YOUR NAME HERE"
output: pdf_assignment
---

### Preliminaries

```{r, message=FALSE, warning=FALSE}
library(MASS)
library(ggplot2)
library(dplyr, warn.conflicts=FALSE)
library(bbmle)
library(interactions)
```

### (1) Log Transformation

a) The `mammals` dataset in the `MASS` package tabulates `body` mass in kg and `brain` mass in g for 62 species of mammals. Plot `brain` (y-axis) against `body` (x-axis).

```{r}
ggplot(mammals, aes(body, brain)) +
  geom_point()
```

b) How does that look?

> 

c) Add new logged body and brain mass variables to the `mammals` data frame.

```{r}
#
```

d) Plot logged brain mass (y-axis) against logged body mass (x-axis)

```{r}
#
```

e) How does that look?

> 

f) Create a linear model to predict brain mass from body mass and generate the summary for that model.

```{r}
#
```

f) Fill in the blank:

> For a 1% change in body mass, the model predicts a _____ change in brain mass.

### (2) Chi-square Goodness of Fit

a) In a standard deck of cards, there are 52 cards: 12 face cards (jacks, queens, kings) and 40 number cards (counting the ace in with the number cards). You are dealt a hand of 10 cards containing no face cards. How would you run a Chi-square goodness of fit to answer the question "Is this consistent with the deck being a standard deck?"

```{r}
#
```

b) Is this consistent with the deck being a standard deck?

> 

### (3) Chi-square Test of Independence / Test of Homogeneity

a) The `survey` dataset in the `MASS` package contains the responses of 237 Statistics students at the University of Adelaide to a number of questions. Here, you will focus on `Sex`, `W.Hnd` (writing hand, `Left` or `Right`), and `Exer` (how often the student exercises: `Freq`, `Some`, `None`). How would you run a Chi-square test to evaluate if males and females are different in their handedness?

```{r}
#
```

b) Do the male and female students differ in handedness according to this test?

> 

c) How would you run a Chi-square test to evaluate if males and females are different in exercise frequency?

```{r}
#
```

d) Do the male and female students differ in exercise frequency according to this test?

> 

e) Leaving the survey data behind, you have painstakingly documented the use of the Oxford comma in 100 primatology and paleoanthropology articles with the following results:

| Article Type      |  Oxford   | No Oxford |
|:------------------|:---------:|:---------:|
| Primatology       |    21     |     29    |
| Paleoanthropology |    33     |     17    |

How would you run a Chi-square test to evaluate if primatology and paleoanthropology differ in their use of the Oxford comma?

```{r}
#
```

f) Do primatology and paleoanthropology differ in their use of the Oxford comma?

> 

### (4) Poisson Regression

Here you will use the built-in `warpbreaks` dataset that tabulate the number of `breaks` in a given length of wool for two different `wool` types (`A` and `B`) and three different loom `tension` settings (`L`, `M`, `H`).

a) Generate a boxplot for these data with `tension` on the x-axis, `breaks` on the y-axis, and with the `wool` types colored differently (either `fill=wool` or `color=wool` in the `aes`thetic).

```{r}
#
```

b) Plot a histogram of the `breaks` - use `binwidth=10`.

```{r}
#
```

Definitely pretty skewed.

c) Create three models to model the number of breaks using a Poisson generalized linear model.
1. with `wool` only as the predictor
2. with `wool` and `tension`
3. with `wool`, `tension`, and their interaction

```{r}
#
```

d) Using either analysis of deviance (through the `anova` function) or AIC/BIC, compare these models.

```{r}
#
```

e) Which is the best fit?

> 

f) Using the `cat_plot` function from the `interactions` package, plot your selected model. The call syntax you want is `cat_plot(model_variable_name, pred=x-axis-variable, modx=split-by-color-variable)` - if that doesn’t help, look at slides 74-76 from the Multiple Linear Regression lecture. Add `geom=”line”` if you like.

```{r}
#
```

g) Compare this model plot to the plot of the observed data that you did in question 4-a. Does the model seem to be capturing the important features of the observed data?

> 
